Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
explain PK terminology

Our tool operates over LLVM bitcode \citep{LLVM_langref,Lattner:2004:LCF:977395.977673}, which is a target for several compilers, most notably Clang (supporting C and C++) and llvm-gcc (supporting C, C++, Fortran and Ada).
Abstract domains are provided by the APRON library \citep{DBLP:conf/cav/JeannetM09}, and include convex polyhedra, octagons, intervals, and linear congruences.
For SMT-solving, our analyzer uses Yices
\cite{DBLP:conf/cav/DutertreM06} or Microsoft Z3\cite{DBLP:conf/tacas/MouraB08}.

@@

Our analysis tool currently only operates over scalar variables from the SSA representation and thus cannot directly cope with arrays or memory accessed through pointers. We therefore run it after the ``memory to registers'' (\texttt{mem2reg}) optimization phase in LLVM, which lifts most memory accesses to scalar variables.
The remaining memory accesses are treated as undefined values, as are the return
values of function calls. For better precision, we also apply function inlining
to the program, and we unroll every loop once.

>>>>

Our tool operates over LLVM bitcode \citep{LLVM_langref,Lattner:2004:LCF:977395.977673}, which is a target for several compilers, most notably Clang (supporting C and C++) and llvm-gcc (supporting C, C++, Fortran and Ada).
Abstract domains are provided by the APRON library \citep{DBLP:conf/cav/JeannetM09}, and include convex polyhedra (from the builtin Polka ``PK'' library), octagons, intervals, and linear congruences.
For SMT-solving, our analyzer uses Yices
\cite{DBLP:conf/cav/DutertreM06} or Microsoft Z3\cite{DBLP:conf/tacas/MouraB08}.

@@

Our tool currently only operates over scalar variables from the SSA representation and thus cannot directly cope with arrays or memory accessed through pointers. We therefore run it after the ``memory to registers'' (\texttt{mem2reg}) optimization phase in LLVM, which lifts most memory accesses to scalar variables.
The remaining memory accesses are treated as undefined values, as are the return
values of function calls. For better precision, we also apply function inlining
to the program, and we unroll every loop once.
